Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-03-10 Thesis/chapter/062-post-emma.tex

\section{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared with EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
combination can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took minimum value from the grid search twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
So 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularisation and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{ccccccc}
        \hline\hline
        method  &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$)   &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $)   &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $)   &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{Best parameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see equations \ref{eq:r2-krr-g}--\ref{eq:r2-svm-p}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.

>>>>

\section{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared 
with the optimization method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
combination can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took minimum value from the grid search twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
So 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{ccccccc}
        \hline\hline
        method  &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$)   &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $)   &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $)   &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{Best parameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see equations \ref{eq:r2-krr-g}--\ref{eq:r2-svm-p}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.
